Joint analysis of read count data

### 2020-09-04 combined_analysis/combine_all_data.Rmd
Fix Dx

```{r differential.expression}

form = ~ Dx*Reported_Gender + RIN + ageOfDeath + scale(IntronicRate)*Cohort + scale(IntragenicRate)*Cohort + scale(IntergenicRate)*Cohort + scale(rRNARate)*Cohort + (1|Region:Cohort) + (1|Institution:Cohort) + (1|Region:Cohort) + (1|Individual_ID)

Lbase = getContrast( vobj, form, METADATA, "RIN")
Lbase[] = 0

L = Lbase
L['Dx_crudeControl'] = 1 
L['Dx_crudeSCZ'] = -1

fit = dream(vobj[1:10,], form, METADATA, BPPARAM = SnowParam(18))

```

>>>>

```{r differential.expression.simple}

form = ~ 0 + Dx + Reported_Gender + RIN + ageOfDeath + scale(IntronicRate)*Cohort + scale(IntragenicRate)*Cohort + scale(IntergenicRate)*Cohort + scale(rRNARate)*Cohort + (1|Region:Cohort) + (1|Institution:Cohort) + (1|Region:Cohort) + (1|Individual_ID)

# get contrasts
Lbase = getContrast( vobj, form, METADATA, "RIN")
Lbase[] = 0

# SCZ
L_SCZ = Lbase
L_SCZ['DxControl'] = -1 
L_SCZ['DxSCZ'] = 1

# BP
L_BP = Lbase
L_BP['DxControl'] = -1 
L_BP['DxBP'] = 1

# BP
L_sex = Lbase
L_sex['Reported_GenderMale'] = 1

L = cbind(	Scz = L_SCZ, 
			BP 	= L_BP, 
			Sex = L_sex)
plotContrasts(L) + theme()

fit_marginal = dream(vobj[1:10,], form, METADATA, L=L,BPPARAM = SnowParam(18))
```
